\documentclass[letterpaper,10pt,titlepage]{article}

\usepackage{graphicx}                                        
                                        
                                       
\usepackage{longtable}
\usepackage{alltt}                                           
\usepackage{float}
\usepackage{color}
\usepackage{url}

\usepackage{balance}
\usepackage[TABBOTCAP, tight]{subfigure}
\usepackage{enumitem}
\usepackage{pstricks, pst-node}

\usepackage{geometry}
\geometry{textheight=8.5in, textwidth=6in}

\newcommand{\cred}[1]{{\color{red}#1}}
\newcommand{\cblue}[1]{{\color{blue}#1}}

\usepackage{hyperref}
\usepackage{geometry}

\def\name{Zixun Lu}

\begin{document}

\begin{titlepage}
    \begin{center}
        \vspace*{1cm}
        \Huge
        \textbf{High Performance XML/XSLT Transformation Server}
        \vspace{0.5cm}
        
        \LARGE
        Benchmark Report \\
        \vspace{1cm}
        CS Senior Capstone \\
        \vspace{1.5cm}

        \textbf{XZES40}
        \date{February, 2017}
        \vfill
        February, 2017
    \end{center}
\end{titlepage}

Benchmark Description:
Our team tests two software. One is Xalan and the other one is Altova. Our client
requires us XZES40 transformer should be worked in Debian system. Only the Xalan
can work in the Debian system. The Altova is worked in Windows platform. Our goal
is that comparing two software which one is faster. After we compare, we can set up a
goal for our application. We use LAN Speed Test to test how long the file can transfer
completely. For the test file, we used simple.xml and simple.xsl which those two files 
are provided in https://github.com/XZES40/XZES40-Transformer/tree/master/xzes40/transformer/examples.

\begin{longtable}{ | p{0.075\linewidth} | p{0.3\linewidth} | p{0.3\linewidth} | p{0.3\linewidth} |} \hline
  Software Name & Stylesheet Compile(1st) & Stylesheet Compile(2nd) & Stylesheet Compile(3rd) \\ \hline
  	Altova &
    0.287s &
    0.287s &
    0.287s \\
  \hline
  	Xalan &
    0.307s &
    0.307s &
    0.307s\\
  \hline
\end{longtable}

Summary:
Because the Altova is not free application so that it is faster than the Xalan application.
Our team will improve the XML/XSLT transform performance by using caching and
parallel method. We will try to finish the output between 0.250 seconds to 0.300 seconds.


\newpage



\end{document}