On the last term, I didn’t mention the XML which are provided by our client are different from simple XML files to our group members.
Those high level XML files are transformed by adding more extra files, like ent and dtd files. 
So I delay the time of developing the application. They have to add those features to this application. 
If we don’t add those features to this application, our application can not transform high level XML files, just only transform simple XML files.
At the beginning of this term, our team finished the whole project. 
I did the bench-marking of our application. 
We our two competitors which are Xalan and Altova. 
One is open source and other one is paying to use. 
Our goal is faster than Xalan. 
But the result of our application transformed time is much faster than Xalan and Altova.
Our application transformed time is 0.110 seconds. 
The Xalan and Altova application are both over 0.300 seconds. 
We think this is different computer configuration effect the final result.
I did the bench-marking of our application in Elijah’s laptop and did the Altova application and Xalan in my laptop. 
His laptop is faster than me. 
We want to make sure the benchmark data is correct and re-do the benchmark for Xalan and Altova application at the same computer configuration laptop. 
At the end, our application is still faster than Xalan and Altova application. 
Our application transformed time is 0.110 seconds and Xalan transformed time is 0.196 seconds. 
The Altova application is 0.161 seconds. Our teams are happy we did the awesome works.
