\subsection{Shuai Peng}

\subsubsection{Fall Term}

\paragraph{2016-10-14}

We meet our sponsor last week, and talk about the Problem Statement, and after that we all signed on that paper.


no problems so far.


Next week, sponsor will provide virtual machine which is Debian Linux system, so we can set up the development environment and ready for the program things.


\paragraph{2016-10-21}
We get the virtual machine and some source file for our project from our sponsor(Steven Hathaway), and we also revise our problem statement.


No problem encountered so far.



We will contact sponsor to sign our revise problem statement, and finish our required document for our project.

\paragraph{2016-10-28}
I write the requirement documents last weeks, and we talk to each other to make sure that we all understand our application. I also set up virtual machine and learn computer system problem.


Requirement documents is lots of pages documents, we spend time on what the specific requirement part.


We will work together to finish our requirement documents next week.

\paragraph{2016-11-04}
We re-write the requirement documents. All of us sit together to think and type this requirement documents.


We have trouble with our performance requirement. I don't know how faster it should be, so I just guess what it is, and we decided to do benchmark.


I think that next week I will write about the technology review.

\paragraph{2016-11-11}
Progress since last week

We discussed our project, and divide into 12 pieces. I am responsible for data transformation, web interface, cache, and Windows install package. Before Friday I have finished web interface part. I will finish other part during weekend.


I get trouble with website interface. I am not sure what is the definition of website interface. I will discuss with my teammate to understand what it is.


For next week, I want to think about the draft of our design document.

\paragraph{2016-11-18}
Last week, we finished the technology review, and we have discussion that talk about design documents.


There is no more problem about our technology review.


We will have draft of design document before Thanksgiving.

\paragraph{2016-11-25}
This week is short week, because of the Thanksgiving day. However, we finish the first draft of our design documents.


We have some problem about that some element in IEEE instruction documents. We will meet TA next week for clearly understand.


We will finish the design documents next week, and ready for the final presentation report.

\paragraph{2016-12-02}
Since last week, our group meet together and write our design documents. We divide design documents as small section, and give each people individuals work. I wrote the cache, parser and website interface part.


There is lots of problem about the design documents. We are not really clearly understand some design viewpoint such as pattern. We asked the TA and understand what is the mean of this design viewpoint.


We plan to finish our final report for this term.
\subsubsection{Spring Term}
\paragraph{2016-01-13}
During this winter break, I did research about the Redis cache manager program. And I also figure out how to run transformer in the virtual machine.


There is no big problem during the winter break.


I create the track tools in GitHub, so we are ready to start our development.

\paragraph{2016-01-20}
I totally understood how to use xalanc++ library to convert xml file and xls file to new xml file. And I have complete part of our basic function for our program.


The xalanc++ API reference is hard to read. We need spend more time to search function that we need.


I will complete the whole basic function for our program. I mean we can transform a document successfully.

\paragraph{2016-01-27}
I have finish the basic idea about our project.


Because I am not familiar with OOP development, so there exist lots of syntax error and type error. I need do lots of debug for fix this problem.


fix the syntax error and type error, and start work on cache.

\paragraph{2016-02-03}
We have debug our main function, and make sure that our program can successfully transfer document.


There still bugs for xalanc++ using, we try to figure it out.


Get ready think about the cache part.

\paragraph{2016-02-10}
During this week, we finally debug our program and complied it successfully. We finish our basically function of our program.


We just over the problem.


We will work on the cache part, and also the assignment of require document.

\paragraph{2016-02-17}
This week our team come together and finish the assignment.


No problem so far


We need finish the cache function and continue our development.

\paragraph{2016-02-24}
Last week I finish the cache code, and there is bug for delete. After I think, I decided that we don't need delete function for cache, we should use wipe function to handle the cache.


Delete get some problem, when we try to free data in cache, we got invalid pointer problem.


Elijah and me will merge cache and daemon together, and we will focus on the future work.


\paragraph{2016-03-03}
This week I didn't do any code work, but I did more research on how to make the program run as parallel computation, because it's new to me, I need do more research on that. After I did research, I think that we should take POSIX Threads as our library to handle parallel computation.


So problem so far.


Maybe write some true code for our project.

\paragraph{2016-03-10}
I wrote a prototype about the parallel computation, this is help us to understand how thread works.


The thread is create before run time, so I try to figure out how to make sure the thread is safely our requirement.


I will finish the parallel computation.

\paragraph{2016-03-17}
We have meet the Steven to talk about the detail of the parallel computation, so I can make better plan and design for the parallel computation, and we come together to finish a draft of poster.


Parallel computation need a good plan to work.


Ready for the demo.

\subsubsection{Spring Term}

\paragraph{2016-04-07}
We just come back and continue to work on our project. In this week, we merge the code what we have, and I was working on parallel computation.


I get trouble with the thread control, I need do research how many thread that we need, and how it work without conflict.


I want finish the parallel computation in next week.

\paragraph{2016-04-14}
The second week, I have finish the parallel computation function for our application. To make sure that function runs correctly, we write a test to test it works or not. Finally, we get the thread working correctly without any crash or error. However it may not really safe, so we need more test in the future.


We meet Steven this week. Steven gives us a new requirement that we need pass the parameter to our transformer for transformation, so I have to do more research on the   file parse. I need figure out how   understand the element.


I want finish the parameter pass for our transformer, so we will finish every basic functionality that we need. The  DTD files is also working, but so far it's not a vital problem for us.

\paragraph{2016-04-21}
Last week I have finished the parameter passing back-end part. C++ file and our transformer is working.


So far, there is no problem for me, however, Elijah get problem on the front-end and web UI, so next week I will help him to finish the web UI.


Because May one is the last day that we submit our work, we want to come together to finish the documentation and do test and debug.

\paragraph{2016-04-28}
Last week, out team did the last fix and improve with our application. We finally fixed the bugs that application has, and Elijah and I finish the documentation.


We get some website interface problems that web interface can not reply correct result from the back-end of the application.


During the weekend, we need do the last check for our program, so it should be ready to release. :)

\paragraph{2016-05-05}
We have submit our project, so we basically didn't change anything last week.


No problem so far.


I think our team should do more test, so we make sure there is no problem during EXPO.

\paragraph{2016-05-12}
Last week, our team come together and finished the progress report. We also discussed about the future work.


No problem so far.


We are ready for the EXPO!

\paragraph{2016-05-19}
Since the last week, we have EXPO,and I just paper for that. I did exercise with my friends.


No problem so far, just need relax, and go to EXPO.


I am ready to write the final report.

\paragraph{2016-05-26}
If I can redo my project, I would tell myself that you should paper everything early, so I can finish my project early and perfectly.


The biggest skills that I have learned is that solving a problem by Google or documentation. This project is really lack of documentation, lots of skill that I have learned come from the stack overflow and such that website.


Both of communication skills and solving problem skills I can use it in the future work.


Sure, I like my project, even it looks boring, but it really train our programming skills.


I learned lots of skills from our teammates, such that communication skills. I never talk to people such that client and high position people, but our teammate has experience, so I learned it.


If I am client of this project, I will be satisfied this project work, because everything that this team did is face my requirement.


If I can continue work it in the future, I would like do more test, fix bugs, and more error catch. Or we can have version 2.0 that it is support multiple platform.


I am little nervous during the EXPO day. This is my first time show my project in that environment. Everyone has interesting project and things, but our project is pure computer working. However, there still some people come to ask our question, this made me feel better. Thus I think that EXPO is a nice place to show our project. :)
