\subsection{Zixun Lu}

\subsubsection{Fall Term}

\paragraph{2016-10-14}
It is first time to meet our client. The client introduced how the project is and what should we in this project.

We don't have any problems so far.

The client will provide the virtual machine to help to set the Debian system. The target platform is Debian operating system. First, we need to run our application in the Debian system. If we have enough time to finish Debian operating system, we may develop other platforms.
\paragraph{2016-10-21}
In this week, our team met our sponsor. The sponsor gave us the virtual machine for our project. So we can use Debian in our computer.

Until now, we don't have any problems.

In the next week, we will write Client Requirement Documents. We will review the feedback in problem statement.
\paragraph{2016-10-28}
We finished the rough draft of Client Requirement Documents.

Other group members did the prefect job. I still need to know more knowledge about XML/XSLT.

We will fix and edit the Client Requirement Document in next week. We also need the signature from our client in the next week.
\paragraph{2016-11-04}
We fix our client requirement document and ask our client some questions to complete our requirement.

We didn't create timeline at the first time, after we discuss and plan, we create the timeline.

We will write technology review next week.
\paragraph{2016-11-11}
Our team divided nine parts in technology review. Each person writes 3 parts. We will discuss and fix after completing technology review.

We don't have any questions for this week but we will meet at Sunday to talk about our technology review.

For next week, we will turn technology review, and get client requirement document's feedback from our TA and fix it. Furthermore, we will plan how to write the preliminary design document.
\paragraph{2016-11-18}
Our team finished the technology review document last week. Our team decided which tools will be used in our application and explain tools in technology review.

We have some problems about format in design document.

We will do the design document in the coming week.
\paragraph{2016-11-25}
We finished the draft of design document.

We had some questions about the format about the design documents and we will ask the TA on the Monday.

First, we will show our works to TA to check our status. We want to get some feedback from our TA to fix our errors. Our team will keep working on the design document.
\paragraph{2016-12-02}
We finished our design document this week and emailed to our client in Thursday, but he didn't reply us.

When we wrote the design document, we confused the format of design document. So our team met our TA in the Monday to ask correct format of design document.

Our team will start the progress report in this week.
\subsubsection{Spring Term}

\paragraph{2016-01-13}
During the winter break, I learned and reviewed the C++ knowledge. I started to use the Debian operation system because our client required us to develop our application in the Debian operation system.

It was my first time to use the Debian operation system and tried to get familiar with the Debian operation system.

I will get to know the Xalan and Xerecs libraries.
\paragraph{2016-01-20}
Our teammates Elijah built the structure of project, we followed the structure and started write the basic function.

Even we wrote the design document, client requirement document and tech-review document, I still confused and struggled to write the real code.

I will try to finish the basic function and look for help from teammates and the Internet.
\paragraph{2016-01-27}
We finished the benchmark report for application and set a goal to compare with Xalan C++.

The Xalan C++ can work in the Debian operation system but the Altova only can work in the Windows system. Our project is requried to develop in the Debian operation system. I'm concerned the Altova date reports will affect the final results.

I will search more XML and XSLT document to make sure that we have enough data to set the goal correctly.
\paragraph{2016-02-03}
Our core function can transfer the XML and XSLT document to a new stylesheet.

I communicated with group members each days but I'm terrible coding ablility delay the progess.

I will keep learning and try my best to fix the bugs.
\paragraph{2016-02-10}
Our team finish and compile successfully the basic transformation. I want to try to fix the debug but it didn't work. It is my problem.

I will improve my coding ability and contribute more.

Our team will finish the midterm progress report for this week.
\paragraph{2016-02-17}
Our team finished the winter midterm progress report and did the presentation in this week.

We don't have too much problems.

We will explore the cache function and start to do the parallel computation.
\paragraph{2016-02-24}
Last week, our team finish the cache function which is one of feature in our application. For me, I did a lots of reasearch on parallel computation.

The parallel computation is hard. First, I want to get fimilar with parallel computation. I start to write sample parallel computation function to make sure I know how to use parallel computation.

Our client provided lots of xml files. I will keep doing benchmark for those files.
\paragraph{2016-03-03}
I finished the benchmark reports and web interface.

The XML files which are provided by our client are not like normal XML files. Those files are relative to the effective xml.base path of the xml document.

Even thought the web interface is finished, I will keep to make it nice and pretty. And I will to learn how to use FPM to create each platforms packages.
\paragraph{2016-03-10}
Our client require me to add comments for each project code by using Doxygen.

Doxygen can't recognized some varaiables name like XZES40.

In the coming week, I will add CGI script to our website interface.
\paragraph{2016-03-17}
We finished the web interface. The web interface can transform the files successfully.

At the beginning, the server didn't get our upload files.

I will start how to build Linux packages in the winter break.
\subsubsection{Spring Term}

\paragraph{2016-04-07}
The break is just end. Our team merge the code and get ready to do the parallel computation.

I have trouble to add CGI sciprt to webiste interface. When I upload XML files to the webiste interace, the website didn't response. 

I will help Shuai to finish the parallel computation. 
\paragraph{2016-04-14}
For this week, our team focus on how to add ent and dtd type files in our application. The dtd file is like css file in html. Right now , our application can completely transfer the XML file to a new XML. After this, I did the benchmark report again for application. Comparing with Xalan and Altova, our application is faster than those two applications.

Our application is much faster than Xalan and Altova. Our application measuring average is 0.152s and Xalan, Altova is over 0.3S. We know our application is faster but it is too faster. We did the benchmark XZES40 application in Elijah and Xalan, Altova in my desktop. We considered the computer configurartion is different and it will cause the measure time.

Our website interface is not perfectly, in the coming week, we need to focus on how to make our website interface perfectly.
\paragraph{2016-04-21}
During the last week, due to laptop configuration(Elijah laptop is faster than my), and I find a same configuration laptop to re-do the benchmark of Altova and Xalan. Proof by facts, our application is the fastest in XML transformation.

Right now, I don't have problems. If my teammates have problems, I would like to help them.

Next week, we need to submit our whole code of application. We want to invite our client to come to school to check our final results.
\paragraph{2016-04-28}
During the last week, our team fix bugs in applications and website interface. And we finished the poster and turned in on Friday. We are excited and ready for the Expo.

Right now, for my part, I totally finished the whole project. I don't have any problems.

For the coming back, our group will test the application again and ready to release.
\paragraph{2016-05-05}
On the last week, our team finish all the coding work and project. Each person wrote WIRED assignment individually.

I don't have any problems right now.

I think for the coming week our team should prepare how to present our application during the Expo. We only have 10 days. We need to practice more.
\paragraph{2016-05-12}
Our team finished the midterm progress report on last week. When we practiced the midterm presentation, we also practiced what should we do on EXPO.

We don't have any problems right now.

The EXPO is coming. We are ready for this.
\paragraph{2016-05-19}
For the last week, our team showed our project in EXPO. There are almost 10 people are interested in our project. I think we did a good job in EXPO.

We don't have any problems during the EXPO.

For the coming back, I will prepare for how to write "three short writings".
\paragraph{2016-05-26}
I will try my best to finish this project. I will review the C Language during the Fall term. Because C Language is the most important tool in our project.

I think I know how to use Xalan transformation and Altova application. And I learn more knowledge on parallel computation and cache method.

In the future, I will try to use Github in command line interface. And I will improve my C language skills.

For our project, I like our transformation can transfer the XML and XSLT files. This transformation is so useful. But I don't like work in Debian operation system. I am a Windows user. Sometimes it is so complex to use this operation system.

My teammates are so great. They teach me how to use the Github in command line interface.

I think our project is fully completed by client's requirement.

Although each users can use our application in the website interface, we still want to develop and build each platform system packages. We want to create an application like Altova did.

Our team is arranged in corner of Kelly building with three electric engineering projects. Their projects are look like cool than us because they have real things to show and children would like to see this. Many people like to ask their project and ignore us. I think it is our problem. We can prepare for some candy for children so we can attract with them.
