%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% What did you learn from all this?
% One per team member.
% > What technical information did you learn?
% > What non-technical information did you learn?
% > What have you learned about project work?
% > What have you learned about project management?
% > What have you learned about working in teams?
% > If you could do it all over, what would you do differently?
% Be honest here -- no B.S.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Zixun Lu}
Our project is developed by C++ language and is run in Debian operation system. I learned a lot of computer technology from this project. The C++ language is the core of this project. This is my first time to develop and create the code. The project is not like an assignment. When you try to do your C++ language assignment in CS161, CS162 and CS 261, the instructor will tell and give you example to help me solving the questions in the assignment. If you don’t know how to solve it, you can get help from TA, your friends and instructor. But project is different. Only your team members and client know how to do it. Sometimes team members don’t know how to do it and I have learn it by myself. I think the Tex is the so useful to write the documents. I never use this tools before I take senior design class. I can write the document in command line interface and create a format document. The another important technology tool is Github. I only uploaded and downloaded the file from the Github by using website interface. My team members taught me how to real using Github by using command line interface. In the Github, when you upload your code to the website, your team members will comment the code. If you have some questions about the project, you can pull the request to look for the help. The Xalan and Altova is two competitors. They are both transformation. The Altova is easy to use. You just need to upload your files and the system will return a transformed file to you. The Xalan is hard to use. I use a lot of time to learn how to use it. The Xalan interface is command line interface. The benchmark files are provided by our client Steven Hathaway. He gave us many of XML and XSLT files. But those XML and XSLT files are not “simple” files. In Altova and Xalan application, I only upload the XML and XSLT files and application will return a transformed XML formatted document. If I want to transfer the files which are provided by our client, I have add ent and dtd type files. After I added the ent and dtd files, the application will return a transformed XML formatted document. XSLT stylesheets can support top-level parameters that are treated as pre-defined variables.  These variables can be given default values within the stylesheet, or use parameter value assignments made available to the application. Xalan supports three types of parameters which are String, Number and Document Fragment. In addition, the ent type files are provided by our client have some errors. From the Altova debugs and error messages, I fixed the bugs in ent files and reported to our client. When I design the website interface, adding the CGI script is the most difficult part. I use the Apache web server so that we can register a script(written in Python) to accept requests and return a response. This is simple, maintainable, and easy to create. This is especially appealing if we are only concerned with implementing the API and not fancy features like accessing a database or storing user sessions. In addition, our client require me to add comments for each project code by using Doxygen. It is not easy to finish this tasks. A special documentation block is a C or C++ style comment block with some additional markings, so doxygen knows it is a piece of documentation that needs to end up in the generated documentation. For Python there is a standard way of documenting the code using so called documentation strings. Such strings are stored in doc and can be retrieved at runtime. Doxygen will extract such comments and assume they have to be represented in a preformatted way. For each code item there are two (or in some cases three) types of descriptions, which together form the documentation: a brief description and detailed description, both are optional. For methods and functions there is also a third type of description, the so called ”in body” description, which consists of the concatenation of all comment blocks found within the body of the method or function. Due to my terrible C++ coding, I delayed the progress of project at the beginning. I tried to debug the teammates bugs but I can’t fix them correctly. I want to thank our captain Elijah. At the beginning, I just know how to upload files to Github by using website interface. He teaches me how to use Git in command line. The Github is not only for uploading the files but also I can comment my teammates code. He is very patient to help me. When I have difficult questions and send messages to him, he always response quickly and correctly. My another teammates Shuai is also a kind person. At the beginning, he developed the basic function for XML transformation without cache function and parallel computation. Because we almost have the same class, we always develop the code together. I think my contribution is lower than my teammates. Because my terrible C++ coding, our teammates have switch their tasks to me. They try to use another way that I can help and contribute to this team. I am really appreciate it. After we switch tasks, our team works is better than in the beginning. If I can do my project all over again, I will try my best to finish this project. I will review the C Language during the Fall term. Because C Language is the most important tool in our project. If I have any questions about the project, I should email the client immediately. Before I join the client meeting, I should prepare some questions to ask client what should I do for the next. Also, managing time is the most important. Doing everything ahead is good for this project.  
