% Section Four: Document Caching
% Owned by Shuai Peng
\subsubsection{XML/XSLT Document Caching}

\paragraph{Option}

There are three technology options for cache.
The first option is storing cache into memory.
The second option is storing our cache in binary file on disk.
The third option is to create database to handle all of data.

\paragraph{Goals for use in design}

Caching is the "plus one" function of XZES40-Transformer application.
Other similar application compile files each time and this wastes a lot of time and resource.
We will create cache to solve this problem. 

\paragraph{Criteria being evaluated}

We want save the time and resources in our XML transformer, so efficiency is the most element that we consider.
This is not only the speed of reading and writing from the cache, we must also weigh the persistence of the cache to avoid recompiling when the system (application or host) is restarted.

\paragraph{Comparison breakdown}

The first option is storing the cache in-memory, this is the faster and easy way to store cache.

The second option is to create a binary file with the cache.
When we are run our application, we read the cache data in from the cache file into memory.
When the cache is updated it is written back to the original file.

The third option technology is that we create database to handle memory.
This spends time to design and create database.

The fourth option is to use the in-memory key-value store Redis \cite{redis} which is a popular for this kind of task.

\begin{center}
    \begin{tabular}{ | l | p{10cm} |}
    \hline
    Technology & Description  \\ \hline

    Memory &
    \begin{itemize}
      \item Application check data from memory, and put cache into memory.
      \item Retrieving data from memory is the faster way.
    \end{itemize} \\ \hline

    Temporary binary file &
    \begin{itemize}
      \item Application loads binary file when it starts. After we close it, application save binary file in external storage driver.
      \item Loading temporary binary file spend time, so it is slower than memory.
    \end{itemize} \\ \hline

    Database &
    \begin{itemize}
      \item Application access data from database.
      \item It takes time to create and manage a database.
    \end{itemize} \\ \hline

    Redis &
    \begin{itemize}
      \item Objects to be serialized before being cached.
      \item Adding an additional dependency to the project.
      \item Less development time spent daemonizing and designing in-memory caching system.
    \end{itemize} \\ \hline
    \end{tabular}
\end{center}

\paragraph{Discussion}

Storing cache into memory is the most easy way, we just need to allocate memory.
However, the main drawback of this technology is when we close application, all of cache data will be wiped out.
We have to compile file next time when we start running the application.
When we are developing the XZES40-Transformer, we find a tools that KeyList is built in XercesC.
This tools is helpful for managing memory, and it has good data structure.

Creating a binary file can avoid losing cache data, but it spends time to load file into memory when application starts.

Creating database is bad option for XZES40-Transformer application because access database spend resource, and it waste time to search cache data.

Redis is an appealing idea, but because it is an additional dependency, and serializing our parsed documents is not something our client wants our application to do, we are not able to pursue it.
If our application had slightly different requirements this may be a viable option.

\paragraph{Selection}

The best option technology is that storing cache into memory.
Although it will lost data after close application, it save the time, and it the faster way.
We may add a 'backup cache' solution to make this the best of both worlds, restoring from the backup when the system restarts but working mostly in-memory.
And we will using KeyList, because it is built in XercesC.
We can just add API, and easy to control the cache storing.
