% Section One: Research and Benchmarking
% Owned by Zixun Lu 
%\section{Research and Benchmarking}
%The first application necessary for XML data processing are XML parsers and XML validators. The key aim is to check correctness of the input data, i.e. their conformance to either W3C recommendations or respective XML schemes. Hence, the benchmarks usually involve sets of correct and incorrect data and the goal is to test whether the application under test recognizes them correctly.
%\subsection{XML Conformance Test Suites}
%Binary tests contain a set of documents of one of the following categories: valid documents, invalid documents, non-well-formed documents, well-formed errors tied to external entity and documents with optional errors. Depending on the category, the tested parser must either accept or reject the document correctly (therefore, the tests are called binary). The expected behavior naturally differs if the tested parser is validating or non-validating. On the other hand, the output tests enable to test whether the respective applications report information as required by the recommendation. Again, validating processors are required to report more information than non-validating ones.
%\subsection{}

%\subsection{}
\section{Research and Benchmarking}

\subsection{Options}

\subsection{Goals for use in design}

Our team will do the research and benchmarking to gurantee our application is the fastest.  

\subsection{Criteria being evaluated}

We will test 10000 requests on three differenet transfomers to find which transformers use the time less. 
At the same time, we test our application by using 10000 requests and compare which use the time less. 

\subsection{Comparison breakdown}


\begin{center}
    \begin{tabular}{ | l | p{10cm} |}
    \hline
    Technology & Description  \\ \hline
    Xalan \cite{Xalan-C} &
    \begin{itemize}
      \item Xalan-C++ uses Xerces-C++ to parse XML documents and XSL stylesheets
      \item Along with a complete API for performing transformations in your C++ applications
      \item Xalan-C++ supports C++ extension functions
    \end{itemize}\\ \hline
    Xerces \cite{Xerces-C} &
    \begin{itemize}
      \item Xerces has rich generating and validating capabilities. 
      \item Building truly internationalized XML applications. 
      \item Building next generation of vertical applications that use XML as their data format. 
    \end{itemize}\\ \hline
    Altova \cite{Altova} &
    \begin{itemize}
      \item To meet industry demands for an ultra-fastor processor
      \item It offers powerful, flexible options for developers including cml, python. 
      \item Superior error reporting capabilities include reporting of multiple errors, detailed error descriptions. 
    \end{itemize}\\ \hline
\end{center}

\subsection{Discussion}
Xalan includes the XSL transformation vocabulary and Xpath, a language for addressing parts of XML documents.
Xerces is a validating XML parser written in a portable subset of C++.  
RaptorXML is built from the ground up to be optimized for the latest standard and parallel computing environments.
\subsection{Selection}

We will use our application to compare those three applications which one is the fastest. 
